\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-30 journalWallFriction/theory2robAlgs.tex
Changed Figure 7 description.

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(17,-3){\small{Case 1: $s_1$ does not hit boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(25,-3){\small{Case 2: $s_1$ hits boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(-6,-3){\small{Polygon generated by first contacts along $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $\overline{ p_i p_{i+1}}$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
 Fig. \ref{fig:polygon} shows six workspaces, their $\Delta$ configuration spaces, and the 2-move reachable sets that correspond to representative initial conditions.
 % The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first. 
Algorithm \ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
The set is constructed by considering each edge of the workspace. We name each vertex as $p_i$ where $1\leq i \leq n$.
  If one particle hits edge $\overline{ p_i p_{i+1}}$ before the other (one particle will always hit before the other unless the particles are parallel to the wall), the corresponding 2-move reachable set is a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
Figure~\ref{fig:polygonAlg} illustrates the procedure to construct the  2-move reachable set generated by collisions with the $\overline{ p_i p_{i+1}}$ edge.
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

Figure \ref{fig:TwoRegions} shows reachable sets for a square workspace. There are four reachable sets, the horizontal (and vertical) reachable sets are equivalent in the  $\Delta$ configuration space so we can plan in this space and choose between the two options to minimize the total distance.

>>>>

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(17,-3){\small{Case 1: $s_1$ does not hit boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(25,-3){\small{Case 2: $s_1$ hits boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(-6,-3){\small{Polygon generated by first contacts along $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $\overline{ p_i p_{i+1}}$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
 Figure \ref{fig:polygon} shows six workspaces, their $\Delta$ configuration spaces, and the 2-move reachable sets that correspond to representative initial conditions.
 Figure \ref{fig:TwoRegions} shows reachable sets for a square workspace. There are four reachable sets, the horizontal (and vertical) reachable sets are equivalent in the  $\Delta$ configuration space so we can plan in this space and choose between the two options to minimize the total distance.
 % The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first. 
Algorithm \ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
The set is constructed by considering each edge of the workspace. We name each vertex as $p_i$ where $1\leq i \leq n$.
  If one particle hits edge $\overline{ p_i p_{i+1}}$ before the other (one particle will always hit before the other unless the particles are parallel to the wall), the corresponding 2-move reachable set is a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
Figure~\ref{fig:polygonAlg} illustrates the procedure to construct the  2-move reachable set generated by collisions with the $\overline{ p_i p_{i+1}}$ edge.
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@
